---
title: "Lab 3: Binomial Regression"
author: "Jaenna Wessling"
date: "2023-01-26"
output: html_document
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)


library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(AICcmodavg)
library(GGally)
library(jtools)
```


# Pseudocode
* Examine our data (plots, tables, summary stats)
* Identify a question
* Wrangle the data
* Identify some candidate models 
* Look at model quality: 
* Select among candidate models using AIC/BIC
* Select among candidate models using K-fold cross validation
* Select among candidate models using area under Receiver Operating Characteristic Curve 


```{r}
# Let's explore our data 
GGally::ggpairs(penguins %>% select(species, bill_length_mm:sex), aes(color = species)) # using colon to call all columns between length - sex

```


```{r}
# Cut down to two most similar species (Chinstrap & Adelie)
class(penguins$species) # tells us it's a factor with different levels to them 
levels(penguins$species) # tells us the different levels (species names)


adelie_chinstrap <- penguins %>% 
  filter(species %in% c('Adelie', 'Chinstrap')) %>% 
  mutate(species = fct_drop(species)) %>%  # take species column, and drop any species that are blank (i.e. Gentoo)
  select(-year) %>% 
  drop_na()
  # %in% function asks each value if 'A' or 'C' is in the vector, instead of == (== means only those that match exactly - lose some of our observations if just saying 'A', 'C')

```



# Let's check out the trends across variables 
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) + 
  geom_point(aes(color = sex, shape = island))  + 
  facet_wrap(~ species) # splits into two plots for each species 


ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = bill_length_mm)) + 
  geom_point(aes(color = sex, shape = island)) + 
  facet_wrap(~ species)
```




## Let's do some binary logistic regression! 
```{r}
# Let's try to predict penguin species by body mass, bill or flipper length & sex 
# How well does the model distinguish between adelie and chinstrap penguins 
# Then compare models 

f1 <- species ~ body_mass_g + flipper_length_mm + sex 

ad_chin_blr1 <- glm(formula = f1, data = adelie_chinstrap, family = 'binomial') # generalized linear model 
# summary(ad_chin_blr1)
# reference level is Adelie
# Body mass is negative, so higher body mass means it's less likely to be a chinstrap & more likely to be Adelie
# Flipper length is positive 1.778e-1, therefore it's more likely to be a chinstrap as flipper length increases 

blr1_tidy <- tidy(ad_chin_blr1)
```




















